\documentclass{LULCSProject}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumitem}
\usepackage{listings, listings-rust, listings-js}
\usepackage{protobuf/lang} 
\usepackage{protobuf/style} 
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{url}
\usepackage{pdfpages}

\newcommand{\tvect}[3] { \ensuremath{\Bigl(\negthinspace\begin{smallmatrix}#1\\#2\\#3\end{smallmatrix}\Bigr)}}
\newcommand{\twovect}[2] { \ensuremath{\left(\negthinspace\begin{smallmatrix}#1\\#2\end{smallmatrix}\right)}}

\title{An Open Source Framework for Building IoT Systems}
\author{Niklas Harnish}
\date{22/03/2024}
%\BSc % \MEng \BEng etc. 
\supervisor{Dr Amna Asif}

\wordcount{0} % number of words in your report 


\abstract{
This project aims to build an open source IoT system, that allows users to easily make their device smart using a framework and connect their device to a premade IoT system. There are three separate parts to this project. The Rust library allows a user to easily create an IoT device using the Rust programming language. The server allows users to connect their IoT device to it. The frontend allows control over devices connected to the server, either through a web interface or from the command-line. This project is meant as a stepping stone, not as a complete system, but as a base for other developers to build on, with easy access to APIs, many examples and an easy-to-use device development library.
}


\declaration{
I certify that the material contained in this dissertation is my own work and does not contain
unreferenced or unacknowledged material. I also warrant that the above statement applies to the
implementation of the project and all associated documentation. Regarding the electronically
submitted work, I consent to this being stored electronically and copied for assessment purposes,
including the School's use of plagiarism detection systems in order to check the integrity of
assessed work.\\
I agree to my dissertation being placed in the public domain, with my name explicitly included
as the author of the work.\\
Name: Niklas Harnish \\
Date: March 22 2024
}

\acknowledgements{
  General acknowledgements \ldots

  your supervisor, your family, your
  friends, \ldots
}

\begin{document}

\maketitle

\pagenumbering{Roman}

\newpage
\listoffigures
\newpage
% \begingroup
% \let\clearpage\relax
%\endgroup

\pagebreak
\pagenumbering{arabic}

%%
%% include your chapters here
%%
\include{chapter_intro}

% Always start your chapter on a new page!
\newpage
\include{chapter_background}

\newpage
\include{chapter_design}

\newpage
\include{chapter_implementation}

\newpage
\include{chapter_testing}

\newpage
\include{chapter_conclusion}

%%
%% You bib file
%%
\newpage
\bibliography{report}

\newpage
\appendix
%%
%% Your appendices
%%
\include{appendix1}
\newpage
\include{appendix2}
\newpage 
\include{appendix3}

\end{document}
